Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-18 main.tex
Comment

Formally, a policy
%
$\pol \in \exists X.\; (\CONTOURS \times \MACHS \rightarrow X)
                       \times (X \rightarrow \CONTOURS)
                       \times (\MACHS \times X \rightharpoonup \MACHS \times X)$
%
comprises
\begin{enumerate*}
  \item a private type $X$ corresponding to an ``implementation'' of the contour,
  \item an initializer: a function taking a contour and a machine state to an initial value of $X$,
  \item a projection: a way of reading a contour out of the private type,
  \item a partial step function of type $(\MACHS \times X) \rightharpoonup X$
    that, when defined, defines the private state after a step of the machine
    (based on the $\stepstounderfull$ relation)
\end{enumerate*}
That is, a policy takes a starting contour and produces a runtime monitor
that carries along some private information and uses it to decide whether to
terminate execution early.

>>>>

Formally, a policy
%
$\pol \in \exists X.\; (\CONTOURS \rightarrow X)
                       \times (X \rightarrow \CONTOURS)
                       \times (\MACHS \times X \rightharpoonup \MACHS \times X)$
%
comprises
\begin{enumerate*}
  \item a private type $X$ corresponding to an ``implementation'' of the contour,
  \item an initializer: a function taking a contour \leo{and a machine state?} to an initial value of $X$,
  \item a projection: a way of reading a contour out of the private type,
  \item a partial step function of type $(\MACHS \times X) \rightharpoonup X$
    that, when defined, defines the private state after a step of the machine
    (based on the $\stepstounderfull$ relation).
    \leo{Not sure this should be taking $\MACHS$ as input. It should take $X$
      plus just the instruction being executed? The rest are the tags in $X$}
\end{enumerate*}
That is, a policy takes a starting contour and produces a runtime monitor
that carries along some private information and uses it to decide whether to
terminate execution early.
